---
title: "Placenta Analysis - Slide Stain Cluster"
author: "Ilya Kukovitskiy"
date: "July 21, 2018"
output: html_document
self_contained: no
---
  
```{r Seeds_Packages,results='hide',message=FALSE}
set.seed(1)
require(cluster)
require(clValid)
require(dplyr)
require(xlsx)
require(ggplot2)
```

# <a id="top"></a>RGB data

[Skip Data Preprocessing](#DatAn)

[Skip to Measuring Clustering Effectiveness](#Measure)

[Skip to Boxplots of Cluster (by Feature)](#Box)

## Data Preprocessing

#### Reading in and storing dataset from file

```{r Reading_Files}
x <- read.csv('ProjectStatistics_UNCSlideStainChar.csv')
# Copying dataset for later exporting
Final <- x
colnames(x)
```

#### Removing undesired variables, scene_name, scene_id, scene_ver

```{r NaN_Column_Removal}
# Removing row 17:
x <- x[,-c(1,2,3)]
```

#### In order to perform cluster analysis, normalizing all columns. Analysis will be performed both on original and scaled data.

```{r Scale}
x.s <- scale(x)
```

[Back to top](#top)

## <a id="DatAn"></a>Data Analysis

### Clustering and Recording Clusters

#### Scaled

```{r Clustering_Scaled}
# hierarchical
hier.s <- hclust(dist(x.s))
HIER.S <- NULL
for(i in 2:12){
  HIER.S <- cbind(HIER.S, cutree(hier.s, k = i) )
}

# kmeans
KMEANS.S <- NULL
for(i in 2:12){
  KMEANS.S <- cbind(KMEANS.S, kmeans(x.s, centers = i)$cluster )
}

# diana
dia.s <- diana(x.s)
DIA.S <- NULL
for(i in 2:12){
  DIA.S <- cbind(DIA.S, cutree(dia.s, i) )
}

# pam
PAM.S <- NULL
for(i in 2:12){
  pam <- pam(x.s, i, cluster.only = TRUE)
  PAM.S <- cbind(PAM.S, pam)
}
rm(pam)
```

#### Unscaled

```{r Clustering_Unscaled}
# hierarchical
hier.u <- hclust(dist(x))
HIER.U <- NULL
for(i in 2:12){
  HIER.U <- cbind(HIER.U, cutree(hier.u, k = i) )
}

# kmeans
KMEANS.U <- NULL
for(i in 2:12){
  KMEANS.U <- cbind(KMEANS.U, kmeans(x, centers = i)$cluster )
}

# diana
dia.u <- diana(x)
DIA.U <- NULL
for(i in 2:12){
  DIA.U <- cbind(DIA.U, cutree(dia.u, i) )
}

# pam
PAM.U <- NULL
for(i in 2:12){
  pam <- pam(x, i, cluster.only = TRUE)
  PAM.U <- cbind(PAM.U, pam)
}
rm(pam)
```

[Back to top](#top)

### <a id="Measure"></a>Measuring Clustering Effectiveness

Several different measures are used. All metrics but Dunn and Silhouette show more stability as the value decreases; Dunn and Silhouette show more stability as the value increases.
Unfortunately, all graphs suggest either two or twelve clusters. This is not reflected in research.

#### Scaled

```{r Scaled_Euclidean}
# Euclidean
Euc.s <- clValid(x.s, 2:12, clMethods = c("hierarchical", "kmeans", "diana", "pam"), validation = c("internal", "stability"), maxitems = 800, metric = "euclidean")
plot(Euc.s)
```

```{r Scaled_Correlation}
# Correlation
Cor.s <- clValid(x.s, 2:12, clMethods = c("hierarchical", "kmeans", "diana", "pam"), validation = c("internal", "stability"), maxitems = 800, metric = "correlation")
plot(Cor.s)
```

#### Unscaled

```{r Unscaled_Euclidean}
# Euclidean
Euc <- clValid(x, 2:12, clMethods = c("hierarchical", "kmeans", "diana", "pam"), validation = c("internal", "stability"), maxitems = 800, metric = "euclidean")
plot(Euc)
```

```{r Unscaled_Correlation}
# Correlation
Cor <- clValid(x, 2:12, clMethods = c("hierarchical", "kmeans", "diana", "pam"), validation = c("internal", "stability"), maxitems = 800, metric = "correlation")
plot(Cor)
```

### Attaching cluster vectors to dataset copies

```{r Attaching_Cluster_Values}
colnames(HIER.S) <- colnames(HIER.U) <- colnames(KMEANS.S) <- colnames(KMEANS.U) <- colnames(DIA.S) <- colnames(DIA.U) <- colnames(PAM.S) <- colnames(PAM.U) <- c("two", "three", "four", "five", "six", "seven", "eight", "nine", "ten", "eleven", "twelve")
# Scaled
Final_Hier.s <- cbind(Final, HIER.S)
Final_Kmeans.s <- cbind(Final, KMEANS.S)
Final_Dia.s <- cbind(Final, DIA.S)
Final_Pam.s <- cbind(Final, PAM.S)
# Unscaled
Final_Hier.u <- cbind(Final, HIER.U)
Final_Kmeans.u <- cbind(Final, KMEANS.U)
Final_Dia.u <- cbind(Final, DIA.U)
Final_Pam.u <- cbind(Final, PAM.U)
```

## Exporting dataset to .csv files

```{r Exporting_File}
# Scaled
try(write.xlsx(Final_Hier.s, "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx"))
try(write.xlsx(Final_Kmeans.s, "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx"))
try(write.xlsx(Final_Dia.s, "ProjectStatistics_UNCSlideStainChar_Cluster_Dia_Scaled.xlsx"))
try(write.xlsx(Final_Pam.s, "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx"))
# Unscaled
try(write.xlsx(Final_Hier.u, "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx"))
try(write.xlsx(Final_Kmeans.u, "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx"))
try(write.xlsx(Final_Dia.u, "ProjectStatistics_UNCSlideStainChar_Cluster_Dia_Unscaled.xlsx"))
try(write.xlsx(Final_Pam.u, "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx"))
```

## Analysis of Clustering

#### Reading in from file

```{r reading_Clusters}
Hier_s <- read.xlsx( "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetIndex = 1)
Kmeans_s <- read.xlsx("ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetIndex = 1)
Diana_s <- read.xlsx("ProjectStatistics_UNCSlideStainChar_Cluster_Dia_Scaled.xlsx", sheetIndex = 1)
Pam_s <- read.xlsx("ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetIndex = 1)
Hier_u <- read.xlsx("ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetIndex = 1)
Kmeans_u <- read.xlsx("ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetIndex = 1)
Diana_u <- read.xlsx("ProjectStatistics_UNCSlideStainChar_Cluster_Dia_Unscaled.xlsx", sheetIndex = 1)
Pam_u <- read.xlsx("ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetIndex = 1)
```

### Summary by Cluster

#### Hierarchical Scaled

```{r Hier_s.Summaries, echo=FALSE}
Hier_s.2 <- group_by(Hier_s, two)
Hier_s.3 <- group_by(Hier_s, three)
Hier_s.4 <- group_by(Hier_s, four)
Hier_s.5 <- group_by(Hier_s, five)
Hier_s.6 <- group_by(Hier_s, six)
Hier_s.7 <- group_by(Hier_s, seven)
Hier_s.8 <- group_by(Hier_s, eight)
Hier_s.9 <- group_by(Hier_s, nine)
Hier_s.10 <- group_by(Hier_s, ten)
Hier_s.11 <- group_by(Hier_s, eleven)
Hier_s.12 <- group_by(Hier_s, twelve)

# two
Summ_Hier_s.2 <- summarise( Hier_s.2, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# three
Summ_Hier_s.3 <- summarise( Hier_s.3, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# four
Summ_Hier_s.4 <- summarise( Hier_s.4, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# five
Summ_Hier_s.5 <- summarise( Hier_s.5, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# six
Summ_Hier_s.6 <- summarise( Hier_s.6, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# seven
Summ_Hier_s.7 <- summarise( Hier_s.7, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eight
Summ_Hier_s.8 <- summarise( Hier_s.8, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# nine
Summ_Hier_s.9 <- summarise( Hier_s.9, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# ten
Summ_Hier_s.10 <- summarise( Hier_s.10, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eleven 
Summ_Hier_s.11 <- summarise( Hier_s.11, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# twelve
Summ_Hier_s.12 <- summarise( Hier_s.12, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
```

#### K-Means Scaled

```{r Kmeans_s.Summaries, echo=FALSE}
Kmeans_s.2 <- group_by(Kmeans_s, two)
Kmeans_s.3 <- group_by(Kmeans_s, three)
Kmeans_s.4 <- group_by(Kmeans_s, four)
Kmeans_s.5 <- group_by(Kmeans_s, five)
Kmeans_s.6 <- group_by(Kmeans_s, six)
Kmeans_s.7 <- group_by(Kmeans_s, seven)
Kmeans_s.8 <- group_by(Kmeans_s, eight)
Kmeans_s.9 <- group_by(Kmeans_s, nine)
Kmeans_s.10 <- group_by(Kmeans_s, ten)
Kmeans_s.11 <- group_by(Kmeans_s, eleven)
Kmeans_s.12 <- group_by(Kmeans_s, twelve)

# two
Summ_Kmeans_s.2 <- summarise( Kmeans_s.2, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# three
Summ_Kmeans_s.3 <- summarise( Kmeans_s.3, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# four
Summ_Kmeans_s.4 <- summarise( Kmeans_s.4, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# five
Summ_Kmeans_s.5 <- summarise( Kmeans_s.5, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# six
Summ_Kmeans_s.6 <- summarise( Kmeans_s.6, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# seven
Summ_Kmeans_s.7 <- summarise( Kmeans_s.7, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eight
Summ_Kmeans_s.8 <- summarise( Kmeans_s.8, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# nine
Summ_Kmeans_s.9 <- summarise( Kmeans_s.9, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# ten
Summ_Kmeans_s.10 <- summarise( Kmeans_s.10, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eleven 
Summ_Kmeans_s.11 <- summarise( Kmeans_s.11, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# twelve
Summ_Kmeans_s.12 <- summarise( Kmeans_s.12, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
```

#### Diana Scaled

```{r Diana_s.Summaries, echo=FALSE}
Diana_s.2 <- group_by(Diana_s, two)
Diana_s.3 <- group_by(Diana_s, three)
Diana_s.4 <- group_by(Diana_s, four)
Diana_s.5 <- group_by(Diana_s, five)
Diana_s.6 <- group_by(Diana_s, six)
Diana_s.7 <- group_by(Diana_s, seven)
Diana_s.8 <- group_by(Diana_s, eight)
Diana_s.9 <- group_by(Diana_s, nine)
Diana_s.10 <- group_by(Diana_s, ten)
Diana_s.11 <- group_by(Diana_s, eleven)
Diana_s.12 <- group_by(Diana_s, twelve)

# two
Summ_Diana_s.2 <- summarise( Diana_s.2, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# three
Summ_Diana_s.3 <- summarise( Diana_s.3, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# four
Summ_Diana_s.4 <- summarise( Diana_s.4, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# five
Summ_Diana_s.5 <- summarise( Diana_s.5, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# six
Summ_Diana_s.6 <- summarise( Diana_s.6, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# seven
Summ_Diana_s.7 <- summarise( Diana_s.7, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eight
Summ_Diana_s.8 <- summarise( Diana_s.8, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# nine
Summ_Diana_s.9 <- summarise( Diana_s.9, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# ten
Summ_Diana_s.10 <- summarise( Diana_s.10, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eleven 
Summ_Diana_s.11 <- summarise( Diana_s.11, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# twelve
Summ_Diana_s.12 <- summarise( Diana_s.12, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
```

#### Pam Scaled

```{r Pam_s.Summaries, echo=FALSE}
Pam_s.2 <- group_by(Pam_s, two)
Pam_s.3 <- group_by(Pam_s, three)
Pam_s.4 <- group_by(Pam_s, four)
Pam_s.5 <- group_by(Pam_s, five)
Pam_s.6 <- group_by(Pam_s, six)
Pam_s.7 <- group_by(Pam_s, seven)
Pam_s.8 <- group_by(Pam_s, eight)
Pam_s.9 <- group_by(Pam_s, nine)
Pam_s.10 <- group_by(Pam_s, ten)
Pam_s.11 <- group_by(Pam_s, eleven)
Pam_s.12 <- group_by(Pam_s, twelve)

# two
Summ_Pam_s.2 <- summarise( Pam_s.2, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# three
Summ_Pam_s.3 <- summarise( Pam_s.3, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# four
Summ_Pam_s.4 <- summarise( Pam_s.4, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# five
Summ_Pam_s.5 <- summarise( Pam_s.5, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# six
Summ_Pam_s.6 <- summarise( Pam_s.6, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# seven
Summ_Pam_s.7 <- summarise( Pam_s.7, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eight
Summ_Pam_s.8 <- summarise( Pam_s.8, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# nine
Summ_Pam_s.9 <- summarise( Pam_s.9, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# ten
Summ_Pam_s.10 <- summarise( Pam_s.10, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eleven 
Summ_Pam_s.11 <- summarise( Pam_s.11, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# twelve
Summ_Pam_s.12 <- summarise( Pam_s.12, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
```

#### Hierarchical Unscaled

```{r Hier_u.Summaries, echo=FALSE}
Hier_u.2 <- group_by(Hier_u, two)
Hier_u.3 <- group_by(Hier_u, three)
Hier_u.4 <- group_by(Hier_u, four)
Hier_u.5 <- group_by(Hier_u, five)
Hier_u.6 <- group_by(Hier_u, six)
Hier_u.7 <- group_by(Hier_u, seven)
Hier_u.8 <- group_by(Hier_u, eight)
Hier_u.9 <- group_by(Hier_u, nine)
Hier_u.10 <- group_by(Hier_u, ten)
Hier_u.11 <- group_by(Hier_u, eleven)
Hier_u.12 <- group_by(Hier_u, twelve)

# two
Summ_Hier_u.2 <- summarise( Hier_u.2, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# three
Summ_Hier_u.3 <- summarise( Hier_u.3, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# four
Summ_Hier_u.4 <- summarise( Hier_u.4, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# five
Summ_Hier_u.5 <- summarise( Hier_u.5, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# six
Summ_Hier_u.6 <- summarise( Hier_u.6, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# seven
Summ_Hier_u.7 <- summarise( Hier_u.7, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eight
Summ_Hier_u.8 <- summarise( Hier_u.8, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# nine
Summ_Hier_u.9 <- summarise( Hier_u.9, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# ten
Summ_Hier_u.10 <- summarise( Hier_u.10, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eleven 
Summ_Hier_u.11 <- summarise( Hier_u.11, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# twelve
Summ_Hier_u.12 <- summarise( Hier_u.12, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
```

#### K-Means Unscaled

```{r Kmeans_u.Summaries, echo=FALSE}
Kmeans_u.2 <- group_by(Kmeans_u, two)
Kmeans_u.3 <- group_by(Kmeans_u, three)
Kmeans_u.4 <- group_by(Kmeans_u, four)
Kmeans_u.5 <- group_by(Kmeans_u, five)
Kmeans_u.6 <- group_by(Kmeans_u, six)
Kmeans_u.7 <- group_by(Kmeans_u, seven)
Kmeans_u.8 <- group_by(Kmeans_u, eight)
Kmeans_u.9 <- group_by(Kmeans_u, nine)
Kmeans_u.10 <- group_by(Kmeans_u, ten)
Kmeans_u.11 <- group_by(Kmeans_u, eleven)
Kmeans_u.12 <- group_by(Kmeans_u, twelve)

# two
Summ_Kmeans_u.2 <- summarise( Kmeans_u.2, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# three
Summ_Kmeans_u.3 <- summarise( Kmeans_u.3, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# four
Summ_Kmeans_u.4 <- summarise( Kmeans_u.4, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# five
Summ_Kmeans_u.5 <- summarise( Kmeans_u.5, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# six
Summ_Kmeans_u.6 <- summarise( Kmeans_u.6, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# seven
Summ_Kmeans_u.7 <- summarise( Kmeans_u.7, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eight
Summ_Kmeans_u.8 <- summarise( Kmeans_u.8, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# nine
Summ_Kmeans_u.9 <- summarise( Kmeans_u.9, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# ten
Summ_Kmeans_u.10 <- summarise( Kmeans_u.10, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eleven 
Summ_Kmeans_u.11 <- summarise( Kmeans_u.11, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# twelve
Summ_Kmeans_u.12 <- summarise( Kmeans_u.12, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
```

#### Diana Unscaled

```{r Diana_u.Summaries, echo=FALSE}
Diana_u.2 <- group_by(Diana_u, two)
Diana_u.3 <- group_by(Diana_u, three)
Diana_u.4 <- group_by(Diana_u, four)
Diana_u.5 <- group_by(Diana_u, five)
Diana_u.6 <- group_by(Diana_u, six)
Diana_u.7 <- group_by(Diana_u, seven)
Diana_u.8 <- group_by(Diana_u, eight)
Diana_u.9 <- group_by(Diana_u, nine)
Diana_u.10 <- group_by(Diana_u, ten)
Diana_u.11 <- group_by(Diana_u, eleven)
Diana_u.12 <- group_by(Diana_u, twelve)

# two
Summ_Diana_u.2 <- summarise( Diana_u.2, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# three
Summ_Diana_u.3 <- summarise( Diana_u.3, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# four
Summ_Diana_u.4 <- summarise( Diana_u.4, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# five
Summ_Diana_u.5 <- summarise( Diana_u.5, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# six
Summ_Diana_u.6 <- summarise( Diana_u.6, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# seven
Summ_Diana_u.7 <- summarise( Diana_u.7, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eight
Summ_Diana_u.8 <- summarise( Diana_u.8, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# nine
Summ_Diana_u.9 <- summarise( Diana_u.9, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# ten
Summ_Diana_u.10 <- summarise( Diana_u.10, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eleven 
Summ_Diana_u.11 <- summarise( Diana_u.11, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# twelve
Summ_Diana_u.12 <- summarise( Diana_u.12, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
```

#### Pam Unscaled

```{r Pam_u.Summaries, echo=FALSE}
Pam_u.2 <- group_by(Pam_u, two)
Pam_u.3 <- group_by(Pam_u, three)
Pam_u.4 <- group_by(Pam_u, four)
Pam_u.5 <- group_by(Pam_u, five)
Pam_u.6 <- group_by(Pam_u, six)
Pam_u.7 <- group_by(Pam_u, seven)
Pam_u.8 <- group_by(Pam_u, eight)
Pam_u.9 <- group_by(Pam_u, nine)
Pam_u.10 <- group_by(Pam_u, ten)
Pam_u.11 <- group_by(Pam_u, eleven)
Pam_u.12 <- group_by(Pam_u, twelve)

# two
Summ_Pam_u.2 <- summarise( Pam_u.2, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# three
Summ_Pam_u.3 <- summarise( Pam_u.3, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# four
Summ_Pam_u.4 <- summarise( Pam_u.4, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# five
Summ_Pam_u.5 <- summarise( Pam_u.5, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# six
Summ_Pam_u.6 <- summarise( Pam_u.6, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# seven
Summ_Pam_u.7 <- summarise( Pam_u.7, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eight
Summ_Pam_u.8 <- summarise( Pam_u.8, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# nine
Summ_Pam_u.9 <- summarise( Pam_u.9, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# ten
Summ_Pam_u.10 <- summarise( Pam_u.10, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# eleven 
Summ_Pam_u.11 <- summarise( Pam_u.11, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
# twelve
Summ_Pam_u.12 <- summarise( Pam_u.12, th_BG.mean = mean(th_BG), th_BG.sd = sd(th_BG), Layer.mean.of.Layer.1..unclassified.mean = mean(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.1..unclassified.sd = sd(Layer.mean.of.Layer.1..unclassified), Layer.mean.of.Layer.2..unclassified.mean = mean(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.2..unclassified.sd = sd(Layer.mean.of.Layer.2..unclassified), Layer.mean.of.Layer.3..unclassified.mean = mean(Layer.mean.of.Layer.3..unclassified), Layer.mean.of.Layer.3..unclassified.sd = sd(Layer.mean.of.Layer.3..unclassified), th_RL1.mean = mean(th_RL1), th_RL2.mean = mean(th_RL2), th_RL3.mean = mean(th_RL3), th_RL1.sd = sd(th_RL1), th_RL2.sd = sd(th_RL2), th_RL3.sd = sd(th_RL3) )
```

### Attaching Summary as Sheets to Corresponding Files

#### Hierarchical Scaled

```{r Hier_s.Summaries_attach, echo=FALSE}
try(write.xlsx(Summ_Hier_s.2, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Two Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.3, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Three Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.4, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Four Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.5, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Five Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.6, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Six Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.7, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Seven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.8, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Eight Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.9, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Nine Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.10, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Ten Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.11, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Eleven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_s.12, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Scaled.xlsx", sheetName="Twelve Cluster Summary", append=TRUE))
```

#### K-Means Scaled

```{r Kmeans_s.Summaries_attach, echo=FALSE}
try(write.xlsx(Summ_Kmeans_s.2, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Two Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.3, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Three Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.4, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Four Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.5, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Five Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.6, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Six Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.7, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Seven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.8, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Eight Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.9, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Nine Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.10, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Ten Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.11, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Eleven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_s.12, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Scaled.xlsx", sheetName="Twelve Cluster Summary", append=TRUE))
```

#### Diana Scaled

```{r Diana_s.Summaries_attach, echo=FALSE}
try(write.xlsx(Summ_Diana_s.2, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Two Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.3, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Three Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.4, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Four Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.5, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Five Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.6, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Six Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.7, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Seven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.8, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Eight Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.9, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Nine Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.10, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Ten Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.11, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Eleven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_s.12, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Scaled.xlsx", sheetName="Twelve Cluster Summary", append=TRUE))
```

#### Pam Scaled

```{r Pam_s.Summaries_attach, echo=FALSE}
try(write.xlsx(Summ_Pam_s.2, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Two Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.3, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Three Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.4, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Four Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.5, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Five Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.6, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Six Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.7, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Seven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.8, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Eight Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.9, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Nine Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.10, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Ten Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.11, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Eleven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_s.12, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Scaled.xlsx", sheetName="Twelve Cluster Summary", append=TRUE))
```

#### Hierarchical Unscaled

```{r Hier_u.Summaries_attach, echo=FALSE}
try(write.xlsx(Summ_Hier_u.2, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Two Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.3, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Three Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.4, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Four Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.5, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Five Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.6, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Six Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.7, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Seven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.8, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Eight Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.9, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Nine Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.10, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Ten Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.11, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Eleven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Hier_u.12, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Hier_Unscaled.xlsx", sheetName="Twelve Cluster Summary", append=TRUE))
```

#### K-Means Unscaled

```{r Kmeans_u.Summaries_attach, echo=FALSE}
try(write.xlsx(Summ_Kmeans_u.2, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Two Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.3, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Three Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.4, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Four Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.5, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Five Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.6, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Six Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.7, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Seven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.8, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Eight Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.9, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Nine Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.10, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Ten Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.11, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Eleven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Kmeans_u.12, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Kmeans_Unscaled.xlsx", sheetName="Twelve Cluster Summary", append=TRUE))
```

#### Diana Unscaled

```{r Diana_u.Summaries_attach, echo=FALSE}
try(write.xlsx(Summ_Diana_u.2, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Two Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.3, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Three Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.4, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Four Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.5, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Five Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.6, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Six Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.7, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Seven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.8, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Eight Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.9, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Nine Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.10, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Ten Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.11, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Eleven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Diana_u.12, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Diana_Unscaled.xlsx", sheetName="Twelve Cluster Summary", append=TRUE))
```

#### Pam Unscaled

```{r Pam_u.Summaries_attach, echo=FALSE}
try(write.xlsx(Summ_Pam_u.2, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Two Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.3, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Three Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.4, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Four Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.5, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Five Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.6, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Six Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.7, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Seven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.8, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Eight Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.9, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Nine Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.10, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Ten Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.11, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Eleven Cluster Summary", append=TRUE))
try(write.xlsx(Summ_Pam_u.12, file = "ProjectStatistics_UNCSlideStainChar_Cluster_Pam_Unscaled.xlsx", sheetName="Twelve Cluster Summary", append=TRUE))
```

[Back to top](#top)

### <a id="Box"></a>Creating Boxplots of Clusters (by Feature)

```{r, Boxplot_function}
Box_by_Cluster <- function(x, Cluster, Cl.type = NULL){
  # factorizing all cluster assingments
  for(V_i in 12:22){
    x[,V_i] <- as.factor(x[,V_i])
  }
  
  # Printing Boxplots
  for(V_i in 5:11){
    V <- colnames(x)[V_i]
    g <- ggplot(x, aes_string(x = Cluster, y = V))
    print(g + geom_boxplot() + 
          labs(title = paste("Box Plot of",Cl.type,"Clustering"),
               x = "Cluster"))
  }
}

Box_all_clusters <- function(x, Cl.type2 = NULL){
  for(Cl.strings in c("two","three","four","five","six","seven","eight","nine","ten","eleven","twelve")){
    print(paste("Summary for",Cl.strings,"clusters."))
    Box_by_Cluster(x, Cl.strings, Cl.type = Cl.type2)
  }
}
```

#### Hierarchical Scaled

```{r Hier_s.Boxplot}
Box_all_clusters(Hier_s, "Hierarchical Scaled")
```

#### K-Means Scaled

```{r Kmeans_s.Boxplot}
Box_all_clusters(Kmeans_s, "K-Means Scaled")
```

#### Diana Scaled

```{r Diana_s.Boxplot}
Box_all_clusters(Diana_s, "Diana Scaled")
```

#### Pam Scaled

```{r Pam_s.Boxplot}
Box_all_clusters(Pam_s, "Pam Scaled")
```

#### Hierarchical Unscaled

```{r Hier_u.Boxplot}
Box_all_clusters(Hier_u, "Hierarchical Unscaled")
```

#### K-Means Unscaled

```{r Kmeans_u.Boxplot}
Box_all_clusters(Kmeans_u, "K-Means Unscaled")
```

#### Diana Unscaled

```{r Diana_u.Boxplot}
Box_all_clusters(Diana_u, "Diana Unscaled")
```

#### Pam Unscaled

```{r Pam_u.Boxplot}
Box_all_clusters(Pam_u, "Pam Unscaled")
```
