---
title: "Placenta Analysis - Slide Stain Cluster"
author: "Ilya Kukovitskiy"
date: "June 24, 2018"
output: html_document
self_contained: no
---
  
```{r,results='hide',message=FALSE}
set.seed(1)
require(cluster)
require(clValid)
```

# RGB data

## Data Preprocessing

#### Reading in and storing dataset from file

```{r}
x <- read.csv('ProjectStatistics_UNCSlideStainChar.csv')
attach(x)
colnames(x)
```

#### Removing undesired variables, scene_name, scene_id, scene_ver

```{r}
# Removing row 17:
x <- x[,-c(1,2,3)]
attach(x)
```

#### In order to perform cluster analysis, normalizing all columns

```{r}
x <- scale(x)
```

## Data Analysis

### There are several different measures of distance between clusters, performing the most common ones: complete, average, and single

```{r}
# complete
hc.complete <- hclust(dist(x), method="complete")
# average
hc.average <- hclust(dist(x), method="average")
# single
hc.single <- hclust(dist(x), method="single")
```

### Plot

```{r}
plot(hc.complete)
plot(hc.average)
plot(hc.single)
# the height represents the distance between clusters
```

### Looks like observation 371 is an outlier, among all clusters. Removing this observation.

```{r}
x1 <- x[-371,]
```

### Clustering and Plotting

```{r}
intern <- clValid(x1, 2:8, clMethods = c("hierarchal", "kmeans", "diana", "sota", "pam"), validation = "internal", maxitems = 800)
summary(intern)
plot(intern)
```

### pam is very similar to kmeans. I will use the simpler and more well-known kmeans algorithm with 2 clusters.

```{r}
K2 <- kmeans(x1, 2)
K2$cluster
```

### Attaching cluster vector to dataset

```{r}
x1k2 <- cbind(x1,K2$cluster)
```

## Exporting dataset to .csv file

```{r}
write.csv(x1, "ProjectStatistics_UNCSlideStainChar_ClusterK2.csv")
```