---
title: "Placenta Analysis - Slide Stain Cluster"
author: "Ilya Kukovitskiy"
date: "July 5, 2018"
output: html_document
self_contained: no
---
  
```{r,results='hide',message=FALSE}
set.seed(1)
require(cluster)
require(clValid)
```

# RGB data

## Data Preprocessing

#### Reading in and storing dataset from file

```{r}
x <- read.csv('ProjectStatistics_UNCSlideStainChar.csv')
# for combining datasets later
P <- read.csv('ProjectStatistics_UNCSlideStainChar.csv')
attach(x)
colnames(x)
```

#### Removing undesired variables, scene_name, scene_id, scene_ver

```{r}
# Removing row 17:
x <- x[,-c(1,2,3)]
attach(x)
```

#### In order to perform cluster analysis, normalizing all columns

```{r}
x <- scale(x)
```

## Data Analysis

### There are several different measures of distance between clusters, performing hierarchical clustering using the most common ones: complete, average, and single

```{r}
# complete
hc.complete <- hclust(dist(x), method="complete")
# average
hc.average <- hclust(dist(x), method="average")
# single
hc.single <- hclust(dist(x), method="single")
```

### Plot

```{r}
plot(hc.complete)
plot(hc.average)
plot(hc.single)
# the height represents the distance between clusters
```

### Looks like observation 371 is an outlier, among all clusters. Removing this observation.

```{r}
#Should I not remove the outlier?

x1 <- x[-371,]
# for combining datasets
P <- P[-371,]
```

### Clustering and Plotting

```{r}
# Euclidean
Euc <- clValid(x1, 2:14, clMethods = c("hierarchical", "kmeans", "diana", "sota", "pam"), validation = c("internal", "stability"), maxitems = 800, metric = "euclidean")
summary(Euc)
plot(Euc)
```

### 

```{r}
# Correlation
Cor <- clValid(x1, 2:14, clMethods = c("hierarchical", "kmeans", "diana", "sota", "pam"), validation = c("internal", "stability"), maxitems = 800, metric = "correlation")
summary(Cor)
plot(Cor)
```

### Attaching cluster vector to dataset

```{r}
x1k2 <- cbind(P,K2$cluster)
```

## Exporting dataset to .csv file

```{r}
write.csv(x1k2, "ProjectStatistics_UNCSlideStainChar_ClusterK2.csv")
```